\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Vijay Kataria} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{Barrack no. 185, Room no. 2,} % Your address
\moveleft.5\hoffset\centerline{Near Sadhubella School, Ulhasnagar - 421001}
\moveleft.5\hoffset\centerline{9850030179}
\moveleft.5\hoffset\centerline{vijay.kataria@ves.ac.in}

%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{OBJECTIVE}  

To explore my potential and channel it in contributing towards the development of an organization while gaining significant experience in the process.

\section{Education}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
\hline
\textbf{Institute} & \textbf{University} & \textbf{Year of passing} & \textbf{Marks Scored} \\
\hline
\textit{Vivekanand Education Society's Institute of Technology} & Mumbai University & 2018 &  8.14 CGPI\\
\textit{Smt. C.H.M College} & H.S.C Board & 2014 & 81.69\% \\
\textit{Pet Oxford High School} & S.S.C Board & 2012 &  87.82\% \\
\hline
\end{tabular}


\section{Projects}

\cventry{Jan'17}{eClassroom}{Final Year Project}{}{}{}
\cvline{}{ \begin{itemize}
    \item Developed a model of classroom where all the classroom activities like - Attendance and Power Management,Changing of Slides from Presentation,Maintenance of eNotes.
    \item Attendance is done by Face Recognition and based on count from server, limited fans and lights are glowed automatically.
   \item Changing of Slides from Presentation and Maintenance of eNotes is done through Speech Commands.
\end{itemize}}

\cventry{Feb'16}{Laboratory Information System}{Android App}{}{}{}
\cvline{}{\begin{itemize}
\item Developed an application which facilitates students and teachers accessing different computers in different laboratories by providing username and password of each computer as well as respective schedule of labs.
\end{itemize}}


\cventry{Nov'16}{Railway Reservation System}{Website}{}{}{}
\cvline{}{ \begin{itemize}
    \item Developed a Website where Passenger can search for all possible destinations of India where they can select date of journey and can download e-ticket. 
\end{itemize}}

\section{Experience}

\cventry{ 5th June’17 to 15th July’17}{At D-KAY Consultancy}{}{}{ Mumbai}{}
\cvline{}{ \begin{itemize}
    \item Implemented Online Sindhi Music Streaming Application named “Sindhyat”
    \item Application developed from website: www.sindhyat.com 
    \item Through this application, User first has to register in app and after logging in, User would be able to play all the songs situated in particular albums. 
	\item User can make own Playlist by adding and removing song from particular album. 
    \item Application found in the PlayStore  with named “Sindhyat”
\end{itemize}}

\cventry{17th July’16 to 16th August’16}{At E-incarnation Pvt. Ltd}{Mumbai}{}{}{}
\cvline{}{ \begin{itemize}
    \item Assembling and Disassembling of the Computers and Laptops. 
    \item  Troubleshooting of problems of Operating Systems like Windows 7, Windows 8 and Windows 10. 
    \item Installation and Configuration of Softwares installations such as MS-Office, Acrobat Reader, Antivirus.

\end{itemize}}
\cvline{}{ Nikhil Vatwani, Vijay Kataria, Richard Joseph, Sujata Khedkar, “Advertisement Suggestions Based on Sentiment Analysis”, International Journal of Innovative Research In Computer and Communication Engineering, Volume 5, Issue 2, February 2017.}

\cvline{}{ e-Classroom technical paper accepted in IEEE exlorer.Yet to be published}

\section{Technology Skills}
\cvline{Programming Skills}{C, Java, PHP}
\cvline{Mobile Skills}{Android, Html5}
\cvline{Web Skills}{CSS, JavaScript}
\cvline{Frameworks}{ Bootstrap}
\cvline{Database Skills}{MySQL, Firebase, SQLite}
\cvline{Tools}{Git, Xampp}

\section{Soft skills}


\cvline{}{ Playing Cricket
Listening Music
Singing
}

\section{Extra Curricular Activities}
\cventry{}{Sports Responsibility Incharge}{}{}{}{}
\cvline{}{ Volunteered in Sphurti (Sports Weekend) in VESIT(2016) }

\cventry{Social Responsibility Incharge}{}{}{}{}{}
\cvline{}{ Volunteered at Zilla Parishad School(NGO), Dombivili-2016  }

\section{Co-Curricular Activities}

\cventry{2016-Present}{ VESIT Societies,
Mumbai}{ISTE and CSI
}{}{}{}
\cvline{}{ Attended various workshops related to technology and Photoshop.}

\cventry{2015}{Leadership Programme,
Mumbai}{Soaring Eagles
}{}{}{}
\cvline{}{ Workshop for Leadership Programming}

\cventry{2016}{Workshops}{Attended Wordpress Workshop at Techzilla}{}{}{}

\section{Personal Information}
\cvline{}{Nationality : Indian}
\cvline{}{Date of Birth : 21st April, 1996}
\cvline{}{Marital Status : Single}

\section{References}
\begin{minipage}[b]{0.33333\textwidth}
\raggedright
Richard Joseph \par
 Professor at Computer Engineering Department, VESIT \par
 8879585434. 
\end{minipage}%
\begin{minipage}[b]{0.33333\textwidth}
\centering
Priya RL \par
Asst. Professor at VESIT \par
priya.rl@ves.ac.in
\end{minipage}%
\begin{minipage}[b]{0.33333\textwidth}
\raggedleft
Deepak Keswani \par
 founder of D-KAY Consultancy Pvt. Ltd  \par
9270014682 
\end{minipage}